|

### 2025-01-14 doc/paper.qmd
paper&readme update

---
title: |
  | Audit market concentration in the EU:
  | Corporate Decision-Making and Quantitative Analysis - Assignment I\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging the Audit Analytics database on Transparency Report data, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization. The project replicates and extends findings from the European Commission’s 2024 report by analyzing and visualizing Big 4, CR4, and 10KAP audit firms’ market shares in the number of public interest entity statutory audits for 2021 across EU countries and at the EU level. The results include a detailed breakdown of market concentration trends, offering insights into the dominance of major audit firms across different jurisdictions. In doing so, the project documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and demonstrates how to structure a reproducible empirical research project. 
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

>>>>

---
title: |
  | How Much New Information Is There in Earnings?
  | Corporate Decision-Making and Quantitative Analysis - 
  | Individual Report\vspace{1cm}
author:
  - name: Melisa Mazaeva
    email: melisa.mazaeva@student.hu-berlin.de
    affiliations:
      - Humboldt-Universität zu Berlin  
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | This project uses the TRR 266 Template for Reproducible Empirical Accounting Research (TREAT) to provide an infrastructure for open science-oriented empirical projects. Leveraging the Audit Analytics database on Transparency Report data, this repository showcases a reproducible workflow that integrates Python scripts for data preparation, analysis, and visualization. The project replicates and extends findings from the European Commission’s 2024 report by analyzing and visualizing Big 4, CR4, and 10KAP audit firms’ market shares in the number of public interest entity statutory audits for 2021 across EU countries and at the EU level. The results include a detailed breakdown of market concentration trends, offering insights into the dominance of major audit firms across different jurisdictions. In doing so, the project documents and discusses the research design choices made and the variations between the original and reproduced results. This code base, adapted from TREAT, provides an overview of how the template can be used for this specific project and demonstrates how to structure a reproducible empirical research project. 
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---
